\documentclass[10pt]{article}

\usepackage[letterpaper,margin=0.32in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[scaled=0.95]{helvet}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage[most]{tcolorbox}
\usepackage{enumitem}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlist[itemize]{leftmargin=1.1em,labelsep=0.4em,itemsep=1.3pt,topsep=2pt,parsep=0pt}

% W.E.T. LAB card palette.
\definecolor{agencyblue}{HTML}{005A8B}
\definecolor{deepsea}{HTML}{143B5D}
\definecolor{labline}{HTML}{A9BBC8}
\definecolor{panelbg}{HTML}{F6F8FA}
\definecolor{titlebg}{HTML}{EAF2F7}
\definecolor{textgray}{HTML}{2F3B45}

\color{textgray}
\tcbset{
  sharp corners,
  boxrule=0.55pt,
  colframe=deepsea,
  colback=white,
  left=6pt,
  right=6pt,
  top=4pt,
  bottom=14pt,
  enhanced
}

\newcommand{\TaskCard}[3]{%
\begin{tcolorbox}[
  height=2.37in,
  valign=center,
  overlay={
    \fill[titlebg] ([yshift=-0.35in]frame.north west) rectangle (frame.north east);
    \draw[labline,line width=0.35pt] ([yshift=-0.35in]frame.north west) -- ([yshift=-0.35in]frame.north east);
    \fill[panelbg] (frame.south west) rectangle ([yshift=0.19in]frame.south east);
    \draw[labline,line width=0.35pt] ([yshift=0.19in]frame.south west) -- ([yshift=0.19in]frame.south east);
    \draw[labline,line width=0.35pt] ([xshift=-0.60in]frame.south east) -- ([xshift=-0.60in,yshift=0.19in]frame.south east);
    \node[anchor=north west,font=\fontsize{7.0}{7.5}\selectfont\bfseries\color{agencyblue}] at ([xshift=5pt,yshift=-4pt]frame.north west) {W.E.T. LAB | CETACEAN CONDITIONING UNIT};
    \node[anchor=north east,font=\fontsize{7.6}{8.0}\selectfont\bfseries\color{deepsea}] at ([xshift=-5pt,yshift=-4pt]frame.north east) {TASK~#1};
    \node[anchor=center,font=\fontsize{5.9}{6.3}\selectfont\bfseries\color{deepsea}] at ([xshift=1.62in,yshift=0.095in]frame.south west) {Approved cues: GOOD DOLPHIN / BAD DOLPHIN};
    \node[anchor=center,font=\fontsize{5.4}{5.9}\selectfont\color{agencyblue}] at ([xshift=-0.30in,yshift=0.095in]frame.south east) {CCU-744-#1};
  }
]
\vspace*{0.17in}
\vfill
\begin{minipage}[c][1.02in][c]{0.84\linewidth}
\centering
{\bfseries\fontsize{10.9}{11.6}\selectfont\color{deepsea} #2\par}
\vspace{6pt}
{\fontsize{7.7}{8.2}\selectfont\bfseries\color{agencyblue}TARGET BEHAVIOR\par}
\vspace{4pt}
\begingroup
\fontsize{9.0}{10.1}\selectfont
\setlength{\parskip}{2.2pt}
\def\item{\par}
#3
\par
\endgroup
\end{minipage}
\vfill
\end{tcolorbox}%
}

\begin{document}
\small

\begin{tcbraster}[
  raster columns=2,
  raster column skip=6pt,
  raster row skip=6pt
]
\TaskCard{01}{The Social Butterfly}{
\item High-five \textbf{3 different people}.
}
\TaskCard{02}{Fashion Evolution}{
\item Put on \textbf{hat + sunglasses}.
}
\TaskCard{03}{Baton Ceremony}{
\item Pick up baton.
\item Hand it to a stranger.
\item Receive it back.
}
\TaskCard{04}{Percussionist}{
\item Play \textbf{drum or maraca}.
\item Continue for at least 5 beats.
}
\TaskCard{05}{Dramatic Entrance}{
\item Leave the area.
\item Re-enter dramatically.
}
\TaskCard{06}{The Recruiter}{
\item Bring \textbf{one new person} back to the team.
}
\TaskCard{07}{Hydration Protocol}{
\item Obtain a drink.
\item Take one sip.
}
\TaskCard{08}{Interpretive Dance}{
\item Perform a 5-second dance.
\item Use the hand fan.
}
\end{tcbraster}

\newpage

\begin{tcbraster}[
  raster columns=2,
  raster column skip=6pt,
  raster row skip=6pt
]
\TaskCard{09}{The Messenger}{
\item Deliver a message to someone across the room.
}
\TaskCard{10}{Sunglass Transfer}{
\item Put on sunglasses.
\item Give them to someone else.
}
\TaskCard{11}{The Parade Leader}{
\item Lead a line of \textbf{2 people}.
\item March for at least 3 steps.
}
\TaskCard{12}{Object Collector}{
\item Gather \textbf{2 different objects}.
\item Bring them back.
}
\TaskCard{13}{Freeze Frame}{
\item Pose like a statue for 5 seconds.
}
\TaskCard{14}{Sound Maker}{
\item Make any non-verbal noise.
\item Repeat 3 times.
}
\TaskCard{15}{The Exchange}{
\item Trade one item with someone.
\item Bring back the new item.
}
\TaskCard{16}{Hat Relay}{
\item Wear a hat.
\item Pass it to 2 different people.
}
\end{tcbraster}

\newpage

\begin{tcbraster}[
  raster columns=2,
  raster column skip=6pt,
  raster row skip=6pt
]
\TaskCard{17}{The Spiral}{
\item Spin in a circle.
\item Then sit or crouch.
}
\TaskCard{18}{The Escort}{
\item Guide someone by gesture.
\item Bring them back to the team.
}
\TaskCard{19}{The Performer}{
\item Use drum or maraca.
\item Get at least 1 person to join.
}
\TaskCard{20}{The Scientist}{
\item Point at 3 different people.
\item Observe them like specimens.
}
\TaskCard{21}{The Mirror}{
\item Copy another person's movement.
\item Continue for 5 seconds.
}
\TaskCard{22}{Fan Operator}{
\item Use hand fan on someone.
\item Continue for 3 seconds.
}
\TaskCard{23}{The Trade Route}{
\item Take an object from Team A.
\item Deliver it to Team B.
}
\TaskCard{24}{The Return Mission}{
\item Leave the team.
\item Touch a wall or object.
\item Return.
}
\end{tcbraster}

\newpage

\begin{tcbraster}[
  raster columns=2,
  raster column skip=6pt,
  raster row skip=6pt
]
\TaskCard{25}{The Mystery Object}{
\item Pick up a random object.
\item Present it to the team.
}
\TaskCard{26}{The Mating Display}{
\item Kiss someone.
\item Cheek is fine.
}
\end{tcbraster}

\end{document}
